---
title: Global Burden of Mental Illnesses
subtitle: Descriptive Statistics Report
author: Aly Lamuri
format: pdf
bibliography: ref.bib
knitr:
  opts_chunk:
    comment: "|"
    echo: false
    error: false
    warning: false
    message: false
---

```{r init}

pkgs <- c("magrittr", "targets", "gtsummary")
pkgs_load <- sapply(pkgs, library, character.only = TRUE)

```

This descriptive statistics on global burden of mental illnesses is reproduced from @owidmentalhealth, where the primary source of data was from the Global Burden of Disease (GBD). This dataset contains 30-year global data from 1990 to 2019 with two mental illness metrics: disability-adjusted life year (DALY) and prevalence. Mental illnesses of interest in this dataset are depressive disorder, anxiety disorder, schizophrenia, bipolar disorder, and eating disorder. @tbl-summary describes the univariable statistics, presented as mean and standard deviation as grouped by the country-level of income. It is notable that each level of income has different prevalence and DALY for mental illnesses. Interestingly, the pairwise correlation between DALY and prevalence, as shown in @tbl-cor-gbd-1 to [-@tbl-cor-gbd-4], indicated different patterns among all level of incomes.

```{r}
#| label: tbl-summary
#| tbl-cap: Descriptive statistics of mental health indicators from GBD dataset

tar_read(gbd_report)

```

```{r}
#| label: tbl-cor-gbd-1
#| tbl-cap: Pairwise correlation of mental illnesses metrics in high-income countries
tar_load(gbd_cor)
knitr::kable(gbd_cor$high_income)

```

```{r}
#| label: tbl-cor-gbd-2
#| tbl-cap: Pairwise correlation of mental illnesses metrics in middle-income countries

knitr::kable(gbd_cor$middle_income)

```

```{r}
#| label: tbl-cor-gbd-3
#| tbl-cap: Pairwise correlation of mental illnesses metrics in lower middle-income countries

knitr::kable(gbd_cor$lower_middle_income)

```

```{r}
#| label: tbl-cor-gbd-4
#| tbl-cap: Pairwise correlation of mental illnesses metrics in low-income countries

knitr::kable(gbd_cor$low_income)

```

# References {-}
